\documentclass[10pt,a4paper]{article}

% ATS-Friendly Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

% Define professional color scheme
\definecolor{headercolor}{RGB}{0, 51, 102}
\definecolor{linkcolor}{RGB}{0, 102, 204}
\definecolor{sectioncolor}{RGB}{0, 51, 102}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    pdfborder={0 0 0}
}

% Remove page numbers
\pagestyle{empty}

% Compact spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% List formatting - very compact
\setlist[itemize]{left=0pt, label=\textbullet, itemsep=1pt, parsep=0pt, topsep=2pt, partopsep=0pt}

% Section formatting
\usepackage{titlesec}
\titleformat{\section}{\color{sectioncolor}\normalsize\bfseries\uppercase}{}{0em}{}[\color{sectioncolor}\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

\titleformat{\subsection}{\small\bfseries}{}{0em}{}
\titlespacing{\subsection}{0pt}{4pt}{2pt}

\begin{document}

%=============================================================================
% HEADER
%=============================================================================
\begin{center}
    {\Large\bfseries\color{headercolor} ADITYA YADAV}\\[3pt]
    Ghaziabad - 201009, India  \\
    \vspace{3pt}
    \href{tel:+91 9717950423}{+91 9717950423} $|$ 
    \href{mailto:adit200515@gmail.com}{adit200515@gmail.com} $|$ 
    \href{https://github.com/Im-diablo}{github.com/Im-diablo} $|$ 
    \href{https://www.linkedin.com/in/aditya-0x/}{linkedin.com/in/aditya-0x} $|$ 
     \href{https://blazedev.in}{blazedev.in} 
\end{center}

 % \vspace{1pt}
%=============================================================================
% OBJECTIVE
%=============================================================================
\section*{Objective}
Innovative CS undergrad, Founder of Codeflow, and NVIDIA-affiliated AI trainee,
seeking to apply expertise in full-stack development, AI/ML
to build impactful, scalable solutions in a forward-thinking organization.

\vspace{3pt}

%=============================================================================
% EXPERIENCE
%=============================================================================
\section*{Experience}
\sectionrule

\noindent\textbf{Founder \& Developer} $|$ \textbf{Codeflow} \hfill \textit{2024 to Present}
\\ Built and delivered websites, apps, and bot marketing solutions to automate client growth.
\vspace{2pt}

\noindent\textbf{Student Trainee} $|$ \textbf{GRIL (NVIDIA Partner)} $|$ \textbf{Global Infoventures} \hfill \textit{2025 -- Present}\\
Selected for an NVIDIA-affiliated training program; working on AI/ML projects and GPU computing with CUDA.

\vspace{3pt}
%=============================================================================
% SKILLS
%=============================================================================
\section*{Skills}
\sectionrule
\textbf{Languages:} C, C++, Java, Python, TypeScript, Dart\\
\textbf{Web \& App:} HTML5, JavaScript, React.js, Flutter, Kotlin\\
\textbf{AI/ML:} OpenCV, Keras, Pandas, NumPy, Matplotlib, Machine Learning\\
\textbf{Database \& Cloud:} MySQL, PostgreSQL, AWS\\
\textbf{Tools \& OS:} Git, GitHub, Android Studio, VS Code, Linux, Windows, LaTeX\\
\textbf{Core Concepts:} Data Structures, OOP, DBMS, Cloud Architecture, Cybersecurity Basics\\
\textbf{Soft Skills:} Leadership, Team Collaboration, Problem Solving, Communication, Adaptability
\vspace{3pt}

%=============================================================================
% PROJECTS
%=============================================================================
\section*{Projects}
\sectionrule
\noindent{\textbf{Sewa Mitr} - A civic issue reporting System.}\hfill \textit{2025}\\
Crowdsourced platform for citizens to report and track civic issues, with automated department routing.\\
\textbf{Tech Stack:} React.js, Flutter, PostgreSQL, Firebase, TypeScript, Vercel, Node.js
\vspace{4pt}

\noindent\textbf{Local LLM Policy Gap Analyzer} \hfill \textit{2026}\\
Offline AI tool that analyzes policy documents and identifies compliance gaps using a local LLM.\\
\textbf{Tech Stack:} Python, PyPDF2, python-docx, Ollama, Gemma3, ReportLab
\vspace{4pt}

\noindent\textbf{Women Safety Analysis System} \hfill \textit{2024}\\
Real-time computer vision system that detects unsafe situations and triggers safety alerts.\\
\textbf{Tech Stack:} Python, OpenCV, Keras, Flask, NumPy, Pandas, Docker, Vercel
\vspace{4pt}

% \noindent\textbf{ERP, Student Management System} \hfill \textit{2024}\\
% Full-stack ERP solution for managing student records, attendance, and automated email notifications.\\
% \textbf{Tech Stack:} PHP, HTML, CSS, JS, MySQL, Nodemailer
% \vspace{3pt}

\noindent\textbf{D-vote, Decentralized Voting System} \hfill \textit{2024}\\
Blockchain-based voting platform ensuring tamper-proof, transparent elections via smart contracts.\\
\textbf{Tech Stack:} Next.js 13, TypeScript, Tailwind CSS, Supabase, MetaMask, CometChat, Solidity, Hardhat, Ethers.js

\vspace{5pt}

%=============================================================================
% Achivements \& Certifications
%=============================================================================
\section*{Achievements \& Certifications}
\sectionrule
\noindent\textbf{Grand Finalist} $|$ \textbf{Smart India Hackathon 2025} \hfill \textit{2025}\\
Developed a Crowdsourced Civic Issue Reporting and Resolution System as part of a six-member team.

\vspace{4pt}
\noindent\textbf{Software Engineering Virtual Experience} $|$ \textbf{JPMorgan Chase \& Co.} \hfill \textit{2026}\\
Configured a Spring Boot (Java 17) backend using Maven for high-volume financial transaction processing.

\vspace{4pt}
\noindent\textbf{Software Architect Virtual Experience} $|$ \textbf{Amazon AWS} \hfill \textit{2025}\\
Completed a Forage virtual job simulation focused on cloud architecture design and AWS-based solutions.

\vspace{4pt}
\noindent\textbf{Cyber Analyst Virtual Experience} $|$ \textbf{Deloitte} \hfill \textit{2025}\\
Completed a virtual job simulation covering cybersecurity fundamentals and OSINT techniques.

\vspace{4pt}
\noindent\textbf{Information Security: Secure Systems Engineering} $|$ \textbf{NPTEL, Govt. of India} \hfill \textit{2025}\\
Completed a government-funded certification on secure systems engineering and information security.

\vspace{5pt}

%=============================================================================
% EDUCATION
%=============================================================================
\section*{Education}
\sectionrule

\noindent\textbf{Bachelor of Technology in Computer Science \& Engineering} \hfill \textit{Expected: 2027}\\
ABES Institute of Technology, Ghaziabad

\vspace{2pt}
\noindent\textbf{Senior Secondary (XII)} \hfill \textit{2023}\\
G.B. Senior Secondary School, Delhi, CBSE

\vspace{2pt}
\noindent\textbf{Matriculation (X)} \hfill \textit{2021}\\
St. Teresa's Convent School, Ghaziabad, ICSE

%=============================================================================
% DECLARATION
%=============================================================================
\section*{Declaration}
\sectionrule
\noindent I hereby declare that all the information provided in this resume is true and correct to the best of my knowledge and belief.
\end{document}
